\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-09 poster/main.tex
update blocks.

\begin{block}{Objectives}
\begin{columns} % Subdivide the first main column
\begin{column}{.69\textwidth}
\begin{enumerate}
\item Designing a differentially private Bayesian inference mechanism.
\item Measuring accuracy with a metric over distributions (Hellinger distance).
\item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
\item Applying smooth sensitivity in mechanism to achieve better accuracy.
        (Fig. \ref{fig_sensitivity} shows that local sensitivity of Hellinger distance is very steep and much higher in the edges but very smooth in central part).
\end{enumerate}
\end{column}
\begin{column}{.28\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.85\textwidth]{poster_0.eps}
say something about beta...
\caption{\footnotesize{Local sensitivity of Hellinger}}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}

@@

\begin{block}{Differentially Private Bayesian inference}
Release a private version of posterior distribution $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.

In a baseline approach, we sample noise from $Lap(\mu,\nu)$ mechanism, i.e., $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$.
Explain parameters of baseline approach...
\end{block}

>>>>

\begin{block}{Objectives}
% \begin{columns} % Subdivide the first main column
% \begin{column}{.69\textwidth}
\begin{enumerate}
\item Designing a differentially private Bayesian inference mechanism.
\item Measuring accuracy with a metric over distributions (Hellinger distance).
% \item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
% \item Applying smooth sensitivity in mechanism to achieve better accuracy.
%         (Fig. \ref{fig_sensitivity} shows that local sensitivity of Hellinger distance is very steep and much higher in the edges but very smooth in central part).
\end{enumerate}
% \end{column}
% \begin{column}{.28\textwidth}
% \begin{figure}[ht]
% \centering
% \includegraphics[width=0.85\textwidth]{poster_0.eps}
% say something about beta...
% \caption{\footnotesize{Local sensitivity of Hellinger}}
% \label{fig_sensitivity}
% \end{figure}
% \vspace{.1cm}
% \end{column}
% \end{columns}

@@

\begin{block}{Differentially Private Bayesian Inference and Motivation}
Release a private version of posterior distribution $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.
\begin{columns} % Subdivide the first main column
\begin{column}{.69\textwidth}
\begin{enumerate}

  \item In a baseline approach, we sample noise from $Lap(\mu,\nu)$ mechanism, i.e., $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$.
  Explain parameters of baseline approach...
  \item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
  \item Applying smooth sensitivity in mechanism to achieve better accuracy.
        (Fig. \ref{fig_sensitivity} shows that local sensitivity of Hellinger distance is very steep and much higher in the edges but very smooth in central part).
\end{enumerate}
\end{column}
\begin{column}{.28\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.85\textwidth]{poster_0.eps}
\caption{\footnotesize{Local sensitivity of Hellinger}}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}
